\begin{enumerate}
	\item \attention GUI - Sun Java 6 (JRE 6), optional: R (see Experiment Mode - README.txt for more details)
	\item \attention {Database - MySQL version 5.1 or above, tested with version 5.1.41 on Ubuntu.
	    The machine the database runs on is the most important factor of the
	    performance of \edacc. The following components will have the greatest
	    impact on database performance:
	    \begin{itemize}
	        \item {The more RAM MySQL can use, the less it has to access slow hard
	            disks on read-transactions. It also enables MySQL to keep indexes and whole tables in memory.
	            This will greatly affect the ability to
	            work on multiple experiments at the same time.}
	        \item {Hard disk performance is not as important as RAM but all data has
	            to be written to the disk eventually which is when fast access time
	            and write throughput become important.}
	        \item {A fast multi-core CPU will enable MySQL to handle more requests concurrently but is
	            not as important as RAM.}
	    \end{itemize}
	    Network latency and bandwidth should also be considered when the GUI and clients
	    are run on remote machines. The clients will write the output of solvers
	    and metadata back to the database so the required bandwidth depends
	    on the size of the generated output and metadata.
	}
	\item Client - see section \ref{clientSR} \attention
	\item Web Frontend - see section \ref{wfSR} \attention
\end{enumerate}
