\upshape
\index{Web Frontend}
\subsection{Introduction}
The Web Frontend provides access to experiment information and analysis tools in a read-only manner
and accessible by a web browser.

\subsection{System requirements}
\label{wfSR}
\index{System requirements, Web Frontend}
The web frontend is implemented as Python WSGI web application and makes use of several libraries.
Since it interfaces with R to draw plots it also depends on R and a Python interface to R, which unfortunately
only works properly on Linux right now.
WSGI applications can be deployed on a variety of web servers or even run standalone on a web server that comes with the
Python standard library.
The following list contains all dependencies and prerequisites of the Web Frontend (see \ref{wf:installation} for installation instructions).
\begin{itemize}
\item Python 2.6.5 or 2.7 http://www.python.org
\item R 2.11 (language for statistical computing and graphics)
\item R package 'np' (available via R's CRAN)
\item SQLAlchemy 0.6.5 (SQL Toolkit and Object Relational Mapper)
\item mysql-python 1.2.3c1 (Python MySQL adapter)
\item Flask 0.6 (Micro Webframework)
\item Flask-WTF 0.3.3 (Flask extension for WTForms)
\item Flask-Actions 0.5.2 (Flask extension)
\item Werkzeug 0.6.2 (Webframework, Flask dependency)
\item Jinja2 2.5 (Template Engine)
\item PyLZMA 0.4.2 (Python LZMA SDK bindings)
\item rpy2 2.1.4 (Python R interface)
\item PIL 1.1.7 (Python Imaging Library)
\item Numpy 1.5.1
\item pygame 1.9 (Graphics library)
\end{itemize}

\subsection{Installation}
\label{wf:installation}
\index{Installation, Web Frontend}
To get rpy2 working the GNU linker (ld) has to be able to find libR.so. Add the folder containing
libR.so (usually /usr/lib/R/lib) to the ld config: Create a file called R.conf containing the
path in the folder /etc/ld.so.conf.d/ and run ldconfig without parameters as root to update.
Additionally, you have to install the R package 'np' which provides non-parametric statistical
methods. This package can be installed by running ''install.packages('np')'' within the R interpreter (as root).

The following installation example outlines the step that have to be taken to install the web frontend on Ubuntu 10.04
running on the Apache 2.2.14 web server. For performance reasons (e.g. query latency) the web frontend should run on the
same machine that the EDACC database runs on.
\marginlabel{\Eexample}
\begin{enumerate}
\item Install Apache and the WSGI module: \begin{verbatim}apt-get install apache2 libapache2-mod-wsgi\end{verbatim}
\item{ Copy the web frontend files to /srv/edacc\_web/, create an empty error.log file and change their ownership to the Apache user: 
\begin{verbatim}
  touch /srv/edacc_web/error.log
  chown www-data:www-data -R /srv/edacc_web
\end{verbatim}
}
\item{ Create an Apache virtual host\\
(new file at /etc/apache2/sites-available/edacc\_web)
\begin{verbatim}
<VirtualHost *:80>
  ServerAdmin email@email.com
  ServerName foo.server.com

  LimitRequestLine 51200000

  WSGIDaemonProcess edacc processes=1 threads=15
  WSGIScriptAlias / /srv/edacc_web/edacc_web.wsgi

  Alias /static/ /srv/edacc_web/edacc/static/

  <Directory /srv/edacc_web>
    WSGIProcessGroup edacc
    WSGIApplicationGroup %{GLOBAL}
    Order deny,allow
    Allow from all
  </Directory>

  <Directory /srv/edacc_web/edacc/static>
    Order allow,deny
    Allow from all
  </Directory>
</VirtualHost>
\end{verbatim}
}
\item{Install dependencies and create a virtual environment for Python libraries:
\begin{verbatim}
apt-get install python-pip python-virtualenv python-scipy
apt-get install python-pygame python-imaging
virtualenv /srv/edacc_web/env
apt-get build-dep python-mysqldb
apt-get install r-base
echo "/usr/lib/R/lib" > /etc/ld.so.conf.d/R.config
ldconfig
source /srv/edacc_web/env/bin/activate
pip install mysql-python
pip install rpy2
pip install flask flask-wtf flask-actions
pip install sqlalchemy pylzma numpy
\end{verbatim}
}
\item{Install R libraries (''R'' launches the R interpreter):
\begin{verbatim}
R
install.packages('np')
\end{verbatim}
}
\item{Create a WSGI file at /srv/edacc\_web/edacc\_web.wsgi with the following contents:
\begin{verbatim}
import site, sys, os
site.addsitedir('/srv/edacc_web/env/lib/python2.6/site-packages')
sys.path.append('/srv/edacc_web')
sys.path.append('/srv/edacc_web/edacc')
os.environ['PYTHON_EGG_CACHE'] = '/tmp'
sys.stdout = sys.stderr
from edacc.web import app as application
\end{verbatim}
}
\item Configure the web frontend by editing /srv/edacc\_web/edacc/config.py, see~\ref{wf:configuration} for details.
\item{Enable the Apache virtual host created earlier:
\begin{verbatim}
a2ensite edacc_web
service apache2 restart
\end{verbatim}
}
\item The web frontend should now be running under http://foo.server.com/
\end{enumerate}

\subsection{Configuration}
\label{wf:configuration}
\index{Configuration, Web Frontend}
All configuration is done in a Python file located at ''edacc/config.py''. The options are documented in the sample configuration
file which is included in the distribution package. Please read through the configuration options and modify those marked as important \attention.
Most importantly, you should disable debugging mode and change the secret key when making the Web Frontend
accessible from the network to avoid security problems. Logging is also quite useful to make it easier to find the cause of bugs in the application.
\marginlabel{Database configuration}At the end of the file you can configure the database connection and the list of EDACC databases that should be
made available by the Web Frontend.

\subsection{Troubleshooting}
\label{wf:troubleshooting}
\index{Troubleshooting, Web Frontend}
When there are errors or bugs and you have set up the Web Frontend under Apache as described in the installation section, Apache will display an ''Internal Server Error'' page.
If you have configured logging, the application will write tracebacks to the logging file. If you haven't set up logging, these tracebacks will end up
in Apache's error.log file.

\subsection{Features}
This section gives a short overview of the features of the Web Frontend. Most features should be self-explanatory or have some additional documentation
on the pages themself.

The Web Frontend was designed as monitoring and analysis tools of experiments that are created with the GUI application. Once you have set up some databases and added
them to the configuration file of the Web Frontend, the top level page will allow the user to select one of the databases. This leads to a page that displays
all experiments of the chosen database and some basic information about their creation date, number of solvers, instances and jobs.

\marginlabel{Experiments}
An experiment page displays further information about the experiment, such as the number of total, running and crashed jobs. If the experiment is currently
being computed, an estimation of the time of completion is displayed next to ''ETA''.

\marginlabel{Monitor progress}
Under ''Progress'' a colored bar visualizes the computation progress.
Green color corresponds to finished jobs, red to crashed jobs and orange to jobs that are currently being computed. The links following the progress bar
lead to information and analysis pages.

\index{Computation progress, Web Frontend}
\marginlabel{Job browser}
The progress page provides a job browser similar to the GUI application. It allows to sort, filter for certain words, show and hide specific columns and download
currently displayed data in CSV (comma-separated values) format\marginlabel{Export data}. Displaying more than 1000 results at once can become rather slow, since the browser's Javascript
engine has to do a lot of processing to color and format the table.

The solver configurations and instances pages show the solver configurations and instances that are part of the experiment. The instances page provides a download link
for all instance files in a tarball\marginlabel{Download instances}.
Instances are shown in a table by name, MD5 checksum and their properties (TODO reference), if there are any. The instance name links to a page that displays the 
first and last few characters of the instance file and provides a download link.

\marginlabel{View results}
\index{Results}
\index{Export results}
The result pages display the results of the jobs in various formats. ''Unsolved instances'' and ''Solved instances'' list the instances that
were not solved by any solver or solved by at least one solver respectively. ''By solver configuration'' leads to a page, where after selecting a solver configuration
that is part of the experiment a table is displayed containing all the results of the jobs of the solver configuration by instance and run number.
''By instance'' leads to a page, where after selecting an instance all results obtained on this instance are displayed by solver configuration and run number.
\marginlabel{Export results}All tables can be exported (i.e. downloaded) in CSV format.

\marginlabel{Analyse results}
\index{Analysis}
\index{Statistical tools}
\index{Visualization}
\index{Plots}
Analysis pages provide various plots of results and statistical tools such as correlation and probabilistic domination calculations. All plots can be directly saved
in PNG format as they are displayed in the browser or downloaded in PDF or EPS format\marginlabel{Export plots}\index{Export plots}. For some plots the application generates an R script which can be adjusted as
neccessary.
Most plots allow to download the underlying data in CSV format.

Some plots allow the selection of multiple instances. In this case, you can use a filter to narrow the selection of the instances listed. Please refer to the example
which is displayed next to the filter text field.

\marginlabel{Ranking of solver configurations}
\index{Ranking}
The ranking is determined by the number of successful runs but the ranking table can be sorted by any of the displayed measures.